Automating Insight Extracting from ML Visual Data with Large Language Models

### 2024-03-01 report/bsc-research-project-proposal.qmd
chore(docs): commit notes & documents

---
title: "Bsc. Research Project Proposal"
author: "Arumoy Shome"
format:
  pdf:
    mainfont: "Iosevka Aile"
    monofont: "Iosevka"
bibliography: bibliography.bib
csl: acm-sig.csl
---

>>>>

---
title: "Automating Insight Extracting from ML Visual Data with Large Language Models"
author: "Arumoy Shome"
format: pdf
bibliography: bibliography.bib
csl: acm-sig.csl
---
